### 2024-09-17 Paper Category/main.tex
New

@@

\section*{Classical gravitational scattering versus Quantum part}

@@

\section*{Holography}
    \item %\cite{Pasterski:2020pdk}
    S.~Pasterski and A.~Puhm,
    ``Shifting spin on the celestial sphere,''
    Phys. Rev. D \textbf{104}, no.8, 086020 (2021)
    doi:10.1103/PhysRevD.104.086020
    [arXiv:2012.15694 [hep-th]].
    69 citations counted in INSPIRE as of 17 Sep 2024\\
    The author aims to  expand the existing framework surrounding conformal primary
    states. They explore conformal primary wavefunctions for all half integer spins up to the graviton within the Celestial Holography program.

\end{itemize}
\end{document}

>>>>

    \item  %\cite{Easson:2023dbk}
    D.~A.~Easson, G.~Herczeg, T.~Manton and M.~Pezzelle,
    ``Isometries and the double copy,''
    JHEP \textbf{09}, 162 (2023)
    doi:10.1007/JHEP09(2023)162
    [arXiv:2306.13687 [gr-qc]].
    18 citations counted in INSPIRE as of 17 Sep 2024\\
    The authors show that the geodicity of the Kerr-Schild vector and the existence of a timelike Killing vector, are in fact consequences of the vacuum conditions instead of assumptions.

@@

\section*{Classical and Quantum gravitational scattering}

@@

    \item %\cite{Kosmopoulos:2023bwc}
    D.~Kosmopoulos and M.~P.~Solon,
    ``Gravitational self force from scattering amplitudes in curved space,''
    JHEP \textbf{03}, 125 (2024)
    doi:10.1007/JHEP03(2024)125
    [arXiv:2308.15304 [hep-th]].
    18 citations counted in INSPIRE as of 17 Sep 2024\\
    The author employ scattering amplitudes in curved space to model the dynamics of a
light probe particle orbiting in the background spacetime.
    \item %\cite{Bern:2023ity}
    Z.~Bern, D.~Kosmopoulos, A.~Luna, R.~Roiban, T.~Scheopner, F.~Teng and J.~Vines,
    ``Quantum field theory, worldline theory, and spin magnitude change in orbital evolution,''
    Phys. Rev. D \textbf{109}, no.4, 045011 (2024)
    doi:10.1103/PhysRevD.109.045011
    [arXiv:2308.14176 [hep-th]].
    21 citations counted in INSPIRE as of 17 Sep 2024\\
    The author clarify the nature of additional Wilson coefficients appear compared to current worldline approaches.
    \item %\cite{Gonzo:2023goe}
    R.~Gonzo and C.~Shi,
    ``Boundary to bound dictionary for generic Kerr orbits,''
    Phys. Rev. D \textbf{108}, no.8, 084065 (2023)
    doi:10.1103/PhysRevD.108.084065
    [arXiv:2304.06066 [hep-th]].
    20 citations counted in INSPIRE as of 17 Sep 2024\\
    The author establish a new relation between classical observables for scattering and bound orbits of a massive probe particle in a Kerr background.

\end{itemize}
\section*{Holography}
\begin{itemize}
    \item %\cite{Pasterski:2020pdk}
    S.~Pasterski and A.~Puhm,
    ``Shifting spin on the celestial sphere,''
    Phys. Rev. D \textbf{104}, no.8, 086020 (2021)
    doi:10.1103/PhysRevD.104.086020
    [arXiv:2012.15694 [hep-th]].
    69 citations counted in INSPIRE as of 17 Sep 2024\\
    The author aims to  expand the existing framework surrounding conformal primary
    states. They explore conformal primary wavefunctions for all half integer spins up to the graviton within the Celestial Holography program.
    \item %\cite{Crawley:2023brz}
    E.~Crawley, A.~Guevara, E.~Himwich and A.~Strominger,
    ``Self-dual black holes in celestial holography,''
    JHEP \textbf{09}, 109 (2023)
    doi:10.1007/JHEP09(2023)109
    [arXiv:2302.06661 [hep-th]].
    19 citations counted in INSPIRE as of 17 Sep 2024\\
    The author use the celestial holography formalism to construct 2D quantum states for 4D linearized rotating self-dual black holes in (2,2) signature Klein space.
\end{itemize}
\section*{Formal Amplitude Method}
\begin{itemize}
    \item  %\cite{Chen:2023dcx}
    A.~S.~K.~Chen, H.~Elvang and A.~Herderschee,
    ``Bootstrapping the String Kawai-Lewellen-Tye Kernel,''
    Phys. Rev. Lett. \textbf{131}, no.3, 031602 (2023)\\
    doi:10.1103/PhysRevLett.131.031602
    [arXiv:2302.04895 [hep-th]].\\
    15 citations counted in INSPIRE as of 17 Sep 2024\\
    This paper extends the minimal rank KLT bootstrap to 6-point, finding novel restrictions on the 4
    and 5-point double-copy maps.
\end{itemize}
\end{document}
